\chapter*{Acknowledgements}

I would like to first thank my advisors, Soren Sorensen, Ken Read, and Christine Nattrass for their time, patience and encouragement. I am so thankful that I had the opportunity to learn from three wonderful advisors that each helped me in a unique way.

Having Dr. Nattrass as a role model and mentor was invaluable. She helped me figure out the tiny details that no one else seemed to have the patience for. 

Dr. Read helped me see the super modules for the towers. I could always rely on him to give me honest feedback and help me figure out the best action to take next.

Dr. Sorensen was simply the best advisor I could ever ask for. I will always have a profound debt of gratitude for his scientific guidance and selfless support and encouragement.

I am so grateful that I had the wonderful opportunity to go to CERN and work among the brilliant physicists that make up the ALICE collaboration. I could not have done this without the hard work from my collaborators, and all the engineers and technicians who contributed to the construction, performance and support of the LHC, the ALICE experiment and the Grid. 

In particular I would like to thank Cristiane Jahnke, Shingo Sakai, and Deepa Thomas who taught and helped me so much.

From the UT and ORNL group, I would like to thank Abhisek Sen, David Silvermyr, Matt Wysocki, Natasha Sharma, and Andrew Castro who helped me at different stages of my analysis.

Thanks to Dr. Marianne Breinig and Chrisanne Romeo who were always willing to help and give advice.

I also would like to thank Kyle Schmoll. When I wanted to quit he gave me the encouragement that I needed to continue on. 

I would like to thank my parents, Dora and Antonino Carnevali, who invested in my education and helped me learn to think like a scientist. I would also like to thank my oldest sibling and best friend Alana, and my favorite and only brother Corey.

Lastly, I would like to thank Neutrino, Cappy and Barlow who gave me unconditional love and companionship throughout my time in graduate school. 