\chapter*{Vita} \label{ch:vita}

%Rebecca Michelle Scott was born in Indiana in 1986. She spent her early childhood in Florence, Alabama and finished high school in 2008 in Morehead Kentucky. Rebecca was encouraged to read books and learn math and science from her mother, who teaches middle school math and science, and her father who was a physics professor.
%
%In college, Rebecca majored in physics and minored in mathematics at Morehead State University in Kentucky. She participated in the Research Experience for Undergraduate program in the summer 2007 at West Virginia University where she studied spintronics and magnetism. At MSU for her senior project, she studied an unusual particle drift in a rotating flow. She graduated from MSU in 2008 and then moved to Tennessee to attend graduate school at the University of Tennessee, Knoxville. 
%
%During her time as a graduate student, Rebecca taught physics labs and won the Outstanding Graduate Teaching Assistant Award in 2009. She joined the UTK Relativistic Heavy Ion Physics group in 2010 to study p+Pb collisions measured by the ALICE experiment at the Large Hadron Collider. Her thesis adviser was Dr. Soren Sorensen.

Rebecca Michelle Scott was born in Indiana in 1986. She spent her early childhood in Florence, Alabama, where she was encouraged to read books and delve into art and the humanities from her middle school math and science teacher mother and her physics professor father. Rebecca's education was achieved in doublets: she attended two elementary schools, two middle schools, two high schools, and two universities. She is now hoping to land two job offers. 

At Morehead State University, in Kentucky, she majored in physics and minored in mathematics. In 2007, she was awarded a Physical Sciences Department scholarship and also participated in the Research Experience for Undergraduate program at West Virginia University, where she studied spintronics and magnetism. For her senior project that same year, she investigated an unusual particle drift in a rotating flow, presented at the SESAPS annual meeting and at the MSU Celebration of Student Scholarship. Upon graduation from MSU in 2008, she enrolled in the PhD program at the University of Tennessee, Knoxville.

During her time as a graduate student, Rebecca taught physics labs and won the Outstanding Graduate Teaching Assistant Award in 2009. She joined the UTK Relativistic Heavy Ion Physics group in 2010 to study p+Pb collisions measured by the ALICE experiment at the Large Hadron Collider. Her thesis adviser was Dr. Soren Sorensen.